---
title       : Peer Assessments
subtitle    : Reproducible Pitch Presentation
author      : Marcus Mariano
job         : Mechanic Engineer
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
ext_widgets : {rCharts: ["libraries/morris","libraries/nvd3", "libraries/polycharts", "libraries/highcharts"]}
knit        : slidify::knit2slides
---

## What is this Presentation?

1. Use as second part of Peer Assessments Course Project of Developing Data Products
2. Objective is show how to simple create an reproducible presentation using Silify
3. This presentation is based on Diamonds dataset
4. Use some R code and graphic

--- .class #id 

## Dataset Presentation

**Summarize the Diamonds dataset**
```{r echo = FALSE}

library(ggplot2); library(rCharts); library(devtools)

```

```{r, echo=TRUE}

str(diamonds)

```

---
## Diamond Weight vs Cut
**Relationship between weight of the diamond and quality of the cut**

```{r, echo = FALSE}

tapply(diamonds$carat, diamonds$cut, mean)

```

```{r chart1, echo = FALSE, eval=TRUE, results = 'asis'}

require(rCharts)
 
diam <- subset(as.data.frame(diamonds), clarity == "I1")

plot_rchar <- nPlot(carat ~ color, group = "cut", data = diam, 
                    type = "multiBarChart")

plot_rchar$print('chart1')
##plot_rchar$show("inline", include_assets = TRUE, cdn = F)


## -------------------


```


--- .class #id 

## Diamond Plot

### Relationship of Price, Carat and Clarity of diamonds in dataset

```{r simple-plot, echo = FALSE, fig.width = 13 , fig.height = 7, fig.align = 'center', message = F}

ggplot(diamonds, aes(x = carat, y = price, color = clarity)) + geom_point()

```


